Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-09-22 nips_2018.tex
long version of the paper

\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
  To evaluate which components of the model are necessary to parse complicated scenes,
  we compared  the neural network
  with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 12$
objects, it successfully parses scenes with many more objects than the
training data.
We compare with a baseline that produces the spec in one shot by
using the CNN to extract features of the input which are passed to an LSTM which finally predicts
the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
but, for this domain, cannot parse cluttered scenes with many objects.
\begin{wrapfigure}{r}{8cm}
  \vspace{0.4cm}
  \centering
      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects. Model generalizes to scenes with many more objects. Neither SMC nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm} 
\end{wrapfigure}

>>>>

\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
  To evaluate which components of the model are necessary to parse complicated scenes,
  we compared  the neural network
  with SMC against the neural network by
itself (i.e., w/ beam search) or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 12$
objects, it successfully parses scenes with many more objects than the
training data.
We compare with a baseline that produces the spec in one shot by
using the CNN to extract features of the input which are passed to an LSTM which finally predicts
the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
but, for this domain, cannot parse cluttered scenes with many objects.
\begin{wrapfigure}{r}{8cm}
  \vspace{0.4cm}
  \centering
      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects. Model generalizes to scenes with many more objects. Neither SMC nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm} 
\end{wrapfigure}
